---
title: "SelfQuant Workflow Example(s)"
author: "Team CityQuant/SelfQuant"
date: "5/26/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Pre-Workflow Setup Steps
1. Download the selfquant package by entering the line devtools::install_github('maczokni/selfquant'). 
2. Make your personal google sheet workbook to track your life. You can do this either by using the createSqTemplate() function within this package or making a duplicate through the Google Sheets UI [here](https://docs.google.com/spreadsheets/d/1ulmrOuD2_jCYJ4TxTVcNZCPqUVR5wxx6DoXW_uz-6lk/edit?usp=sharing)

## Pull the current month from google sheets

```{r}
library(googlesheets)
library(dplyr)
library(selfquant)

#Authenticate R to look at my Google Docs
(my_sheets <- gs_ls())
#Pull my custom tracker to look at May data
sq_data <- getQuant(title = "Chelsea Quant", workSheet = "0517")

#calculate summary stats
summary_df <- calcSummary(sq_data)

#Plot the month's data
#plotWeek(summary = summary_df)
```



